Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/ClementiBarba2020.tex
add to abstract

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    related. This paper presents validation and replication studies in 
    electromagnetic excitations on nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software PyGBe: a boundary element
    solver with trecode acceleration and GPU capability.
    We replicate a result by Rockstuhl et al. (2005, doi:10/dsxw9d) with a
    two-dimensional boundary element method on silicon carbide particles,
    despite differences in our method. 
    The second replication case from Ellis et al. (2016, doi:10/f83zcb) looks
    at aspect ratio effects on high-order modes of localized surface phonon-polariton
    nanostructures. The results partially replicate: the wavenumber
    position of some mode match, but for other modes they differ.
    With virtually no information about the original simulations, 
    explaining the discrepancies is not possible. 
    A comparison with experiments that measured polarized reflectance 
    of silicon carbide nano pillars provides a validation case.
    The wavenumber of the dominant mode and two more do match, but 
    differences remain in other minor modes.

@@

Some fields of research, particularly solid mechanics and computational fluid dynamics, have a long tradition of community consensus building and established practices for verification and validation of computational models. 
Such practices are uncommon in other fields of science, especially if they have more recently become computationally intensive.
Verification and validation also become increasingly difficult when the computational models arise from many levels of mathematical and physical modeling, representing a complex system. 
In recent years, science as a whole has come to be concerned with reproducibility and replication as a new front in the continual campaign to build confidence on published findings. 
Together with formal processes of uncertainty quantification, we have now three complementary ``axes'' to building trust in science.

>>>>

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    related. This paper presents validation and replication studies in 
    electromagnetic excitations on nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software PyGBe: a boundary element
    solver with trecode acceleration and GPU capability.
    We replicate a result by Rockstuhl et al. (2005, doi:10/dsxw9d) with a
    two-dimensional boundary element method on silicon carbide particles,
    despite differences in our method. 
    The second replication case from Ellis et al. (2016, doi:10/f83zcb) looks
    at aspect ratio effects on high-order modes of localized surface phonon-polariton
    nanostructures. The results partially replicate: the wavenumber
    position of some mode match, but for other modes they differ.
    With virtually no information about the original simulations, 
    explaining the discrepancies is not possible. 
    A comparison with experiments that measured polarized reflectance 
    of silicon carbide nano pillars provides a validation case.
    The wavenumber of the dominant mode and two more do match, but 
    differences remain in other minor modes. 
    Results in this paper were produced with strict reproducibility
    practices, and we share reproducibility packages for all, including
    input files, execution scripts, secondary data, post-processing code and
    plotting scripts, and the figures (deposited in Figshare and Zenodo).
    In view of the many challenges faced, we propose that reproducible
    practices make replication and validation more feasible.

@@

Some fields of research, particularly solid mechanics and computational fluid dynamics, have a long tradition of community consensus building and established practices for verification and validation of computational models. 
Such practices are uncommon in other fields of science, especially if they have more recently become computationally intensive.
Verification and validation also become increasingly difficult when the computational models arise from many levels of mathematical and physical modeling, representing a complex system. 
In recent years, science as a whole has come to be concerned with reproducibility and replication as a new front in the continual campaign to build confidence on published findings. 
Together with formal processes of uncertainty quantification, we have now three complementary ``axes'' for building trust in science.

### 2020-07-27 tex/discussion.tex
add to abstract

Validation has been a hard goal to achieve for our solver since the field does not have benchmarks that are meant to be used for validation. Multiple times,
we encountered experimental results that we aspired to replicate, but due to the insufficient reporting of the experimental conditions, the setup and the geometries involved, 
we have unable to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors of Ellis et al., made 
the validation possible.

>>>>

Validation has been a hard goal to achieve for our solver since the field does not have benchmarks that are meant to be used for validation. Multiple times,
we encountered experimental results that we aspired to replicate, but due to the insufficient reporting of the experimental conditions, the setup and the geometries involved, 
we have been unable to validate until this moment. Even though we were not modeling the same experimental setup, the communications with the authors of Ellis et al., made 
the validation possible.
